\chapter{The Seven Core Phrases}

\section{Core Heads}

The argument identifies seven core verbal heads in Revelation 1:1--2. The first six belong to the transmission sequence. The seventh names John's reception.

\begin{center}
\begin{longtable}{@{}L{0.16\textwidth}L{0.2\textwidth}L{0.22\textwidth}L{0.3\textwidth}@{}}
\toprule
Head & Form & Function & Reason for inclusion \\
\midrule
\textit{apokalypsis} & noun & disclosure / truth-claim communication & An eventive noun at the head of the passage. \\
\textit{edoken} & finite verb & giving / transfer & God gives the disclosure to someone. \\
\textit{deixai} & infinitive & showing / communication to consciousness & The giving has the purpose of showing the servants. \\
\textit{esemanen} & finite verb & signifying / communication to consciousness & The act is stated, but its dependents are compressed. \\
\textit{aposteilas} & participle & sending / transfer & The sending phrase belongs to the same communicative movement. \\
\textit{emartyresen} & finite verb & testimony / truth-claim communication & John testifies to named contents. \\
\textit{eiden} & finite verb & reception & John sees what is communicated. \\
\bottomrule
\end{longtable}
\end{center}

\section{Transmission And Reception}

The distinction between transmission and reception prevents the system from counting every verbal element in the same way. \textit{Apokalypsis}, \textit{edoken}, \textit{deixai}, \textit{esemanen}, \textit{aposteilas}, and \textit{emartyresen} form the communicative and transfer movement. \textit{Eiden} is necessary, but it does not perform the same kind of transmission act. It names the receiving side of the process.

\begin{center}
\begin{longtable}{@{}L{0.18\textwidth}L{0.42\textwidth}L{0.3\textwidth}@{}}
\toprule
Head & Surface phrase & Immediate pressure \\
\midrule
\textit{apokalypsis} & \textit{apokalypsis Iesou Christou} & The genitive relation must be determined. \\
\textit{edoken} & \textit{hen edoken auto ho theos} & The referent of \textit{auto} must be identified. \\
\textit{deixai} & \textit{deixai tois doulois autou ha dei genesthai en tachei} & The subject of showing is not newly expressed. \\
\textit{esemanen} & \textit{kai esemanen} & Subject, object, and recipient are not fully expressed. \\
\textit{aposteilas} & \textit{aposteilas dia tou angelou autou to doulo autou Ioanne} & The sender, object, and function of sending must be determined. \\
\textit{emartyresen} & \textit{hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou} & The testimony objects must be related. \\
\textit{eiden} & \textit{hosa eiden} & What John saw must be related to what John testified. \\
\bottomrule
\end{longtable}
\end{center}
