\chapter{Reduced And Expanded Forms}

\section{Reduced Form}

The reduced form is the compact surface form. It is the form the reader receives before the argument supplies any recoverable dependents.

\begin{quote}
\textit{Apokalypsis Iesou Christou hen edoken auto ho theos deixai tois doulois autou ha dei genesthai en tachei, kai esemanen aposteilas dia tou angelou autou to doulo autou Ioanne, hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou hosa eiden.}
\end{quote}

\section{Expanded Form}

The expanded form marks only those elements that the argument treats as recoverable from corresponding phrases in the structure. Brackets mark supplied constituents.

\begin{quote}
\textit{[Ton logon tou theou kai ten martyrian Iesou Christou] apokalypsis Iesou Christou hen edoken auto ho theos deixai tois doulois autou ha dei genesthai en tachei, kai [tois doulois autou ha dei genesthai en tachei] esemanen aposteilas [hen] dia tou angelou autou to doulo autou Ioanne, hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou hosa eiden.}
\end{quote}

\section{Source Of Each Supply}

\begin{center}
\begin{longtable}{@{}L{0.22\textwidth}L{0.34\textwidth}L{0.34\textwidth}@{}}
\toprule
Supplied constituent & Source in the surface form & Reason for recovery \\
\midrule
\textit{ton logon tou theou kai ten martyrian Iesou Christou} & A' testimony phrase & \textit{Apokalypsis} and \textit{emartyresen} correspond as truth-claim communication terms. \\
\textit{tois doulois autou ha dei genesthai en tachei} & C showing phrase & \textit{Deixai} and \textit{esemanen} correspond as communication terms directed toward consciousness. \\
\textit{hen} & B giving phrase & \textit{Edoken} and \textit{aposteilas} correspond as transfer terms; what is given is the recoverable object of sending. \\
\bottomrule
\end{longtable}
\end{center}

\section{Limits}

The expanded form does not add a printed subject before \textit{deixai}. It does not force \textit{eiden} into the six-part chiasm. It does not add \textit{te} to the base text. It does not turn every later interpretive question into a solved question. Its function is narrower: it displays what the reduced form contains when recoverable dependents are supplied by the passage's own correspondences.
