\chapter{Linguistic Concepts Used In The Book}

\section{Reduced Form}

The reduced form is the compact surface form of the passage. It is not a shorter version of the text and not a damaged text. It is the form in which the Greek presents the opening before the interpreter supplies unstated subjects, objects, recipients, or relations.

\section{Expanded Form}

The expanded form is an analytical reconstruction. It displays recoverable dependents that the argument claims are supplied by the passage's own structure. It is not a replacement Greek text and not a paraphrase.

\section{Head And Dependent}

A head is the controlling word of a phrase or clause-like unit. A dependent is an element that belongs to that head, such as a subject, object, recipient, modifier, or complement. In the phrase ``God gave the disclosure,'' the verb ``gave'' functions as a verbal head, while ``God'' and ``the disclosure'' are dependents.

\section{Core Verbal Head}

A core verbal head is a term that names a main occurrence in the opening's communicative movement. The term can be a finite verb, infinitive, participle, or eventive noun. The category is functional, not merely formal. \textit{Apokalypsis} is included because it names an eventive disclosure; \textit{eiden} is included because it names John's reception.

\section{Ellipsis}

Ellipsis occurs when something expected for full expression is omitted because it is recoverable. The omitted element should not be supplied from convenience. It should be recovered from textual controls. In Revelation 1:1--3, \textit{kai esemanen} is a major test case because the phrase states the act of signifying without fully expressing subject, object, and recipient in the immediate phrase.

\section{Chiasm}

A chiasm is an inverted arrangement, often described as A-B-C-C'-B'-A'. The value of a chiasm depends on whether the corresponding elements are real and whether the structure explains something. In this book, the proposed chiasm matters only because the corresponding pairs govern recoverability.

\section{Eventive Noun}

An eventive noun is a noun that names an act, occurrence, process, or event. \textit{Apokalypsis} is grammatically a noun, but it names a disclosure. That eventive force is why the opening term can participate in the communication sequence without being treated as a finite verb.

\section{Transmission And Reception}

Transmission names the movement by which the disclosure is given, shown, signified, sent, and testified. Reception names the receiving side of that movement. John sees; readers hear; hearers keep. The argument distinguishes transmission from reception so that \textit{eiden} can matter without being forced into the six-part transmission chiasm.

\section{Governance}

Governance means that an interpretive decision is controlled by a stated rule or structure rather than by plausibility alone. A reading may be possible and still under-governed. The goal of the argument is not to multiply possibilities, but to show which supplies the structure permits and which it excludes.
