\chapter{What Counts As An Interpretation System?}

\section{From Possibility To Constraint}

The previous chapter argued that the familiar readings of Revelation 1:1--3 are often plausible. That matters because the book is not helped by pretending that the mainstream reading is absurd. It is not. The opening can be read as a linear chain in which God gives a revelation to Jesus Christ, Jesus Christ shows it to his servants, Jesus Christ makes it known by sending an angel to John, and John passes it on to the churches. That reading has coherence.

But coherence is not the same as constraint. A reading is coherent when its parts can be made to fit together. A reading is constrained when the text itself requires those parts to fit in that way and not in another. The difference is essential. Many interpretations become coherent after the interpreter has made enough decisions. The question is whether the decisions were governed before the interpretation became smooth.

This book therefore distinguishes three levels of judgment. The first is grammatical possibility. A phrase can be grammatically possible when Greek allows it. The second is contextual plausibility. A phrase can be contextually plausible when it fits the surrounding argument, theology, or expected sequence. The third is system-governed conclusion. A conclusion is system-governed when a stated method explains why that reading is chosen and why rival plausible readings are excluded.

The first two levels are important, but they do not finish the task. If \textit{apokalypsis Iesou Christou} can be understood in more than one way, grammar has opened a field of possibilities. If one of those possibilities fits the familiar communication chain, context may make it attractive. But only a system can explain why that attractive reading should control the rest of the sentence.

The same applies to \textit{auto}, \textit{deixai}, \textit{esemanen}, \textit{aposteilas}, the servants, and \textit{en tachei}. Each can be given a plausible interpretation. The problem is not shortage of plausible interpretations. The problem is excess. When several readings are possible, interpretation needs more than preference, habit, or theological convenience. It needs constraints.

Constraint does not mean that every reader must find the argument obvious. The expanded form this book will later propose is not obvious at first glance. If it were, the history of interpretation would look different. Constraint means that the steps from the surface form to the conclusion are ordered, repeatable, and open to testing. The reader should be able to see what evidence is being used, what rule is being applied, and what would count against the proposal.

\section{Rules, Economy, And Exclusion}

An interpretation system needs rules. A rule is not a slogan or a preference. It is a repeatable instruction for moving from evidence to conclusion. If a rule applies to one phrase but disappears when it becomes inconvenient for another phrase, it is not governing the interpretation. It is decorating it.

The first requirement is predictability. Similar evidence should produce similar interpretive moves. If ellipsis in one phrase allows missing dependents to be recovered from a corresponding phrase, the same kind of recovery should be tested wherever the same conditions appear. If a pronoun is interpreted by structural relation rather than by nearest familiar antecedent, that standard should not be abandoned as soon as another pronoun or possessive creates pressure.

The second requirement is consistency. Consistency does not mean that every phrase must behave identically. Revelation 1:1--3 is not a machine with interchangeable parts. It contains finite verbs, an infinitive, a participle, a verbal noun, a relative clause, and a final testimony clause. A good system must respect those differences. But it should not change its method without reason. It should not decide one phrase by grammar, another by inherited translation, another by theology, and another by convenience while pretending that all decisions have the same status.

The third requirement is economy. Economy asks whether the interpretation uses what the passage already provides before importing new assumptions. If the surface form leaves a subject or object unexpressed, the first question should be whether the surrounding structure supplies it. If a phrase has a corresponding phrase, that correspondence should be tested before a new participant or object is introduced. Economy does not mean the shortest explanation is always right. It means the interpretation should not multiply solutions when the passage itself offers a more controlled one.

The fourth requirement is exclusion. This may be the most important. A system that cannot exclude a plausible reading has not solved the problem of plausibility. It has only arranged options. If ``from Jesus Christ,'' ``about Jesus Christ,'' ``belonging to Jesus Christ,'' and a layered reading of \textit{Iesou Christou} are all grammatically possible, a system must eventually say which reading the structure validates and which readings it excludes for this passage. Otherwise the reader is left with a list of possibilities rather than an interpretation.

Exclusion also guards against a false kind of fairness. It can sound modest to say that every plausible reading remains possible. But if the text has a structure that decides among them, refusing to decide is not humility. It is a failure to let the text govern. The goal is not to be severe for its own sake. The goal is to allow the passage's own constraints to have consequences.

This means the system proposed in this book must itself be vulnerable. It cannot merely point to patterns that look interesting. It must state what the patterns do. It must explain which dependents can be supplied, which cannot, and why. It must distinguish the parts of the case that carry the most weight from those that are supporting or secondary. A system that cannot be tested cannot require assent.

The system will not claim perfect symmetry. That matters. Some arguments fail because they promise more neatness than the text provides. The opening of Revelation contains compression, variation, and at least one element that stands outside the chiastic nucleus the book will later identify. A system can be real without being perfectly symmetrical. Its strength lies not in making every detail look identical, but in explaining more of the passage with fewer arbitrary moves.

\section{The Order Of Inquiry}

The order of inquiry matters because the order of inquiry often determines the result. If theology is allowed to decide the pronoun before the grammar and structure have been examined, the later analysis will merely confirm what has already been assumed. If intertextual echoes are allowed to decide the structure before the local syntax is tested, the reader may never see what the opening itself is doing. If translation tradition is treated as the starting point, the Greek may be asked only to justify what English has already made familiar.

The order used in this book is deliberately slower.

First comes the local Greek. The words, phrases, clauses, and relations in Revelation 1:1--3 must be observed before they are harmonized with larger expectations. This includes the ambiguity of \textit{apokalypsis Iesou Christou}, the pronoun \textit{auto}, the purpose infinitive \textit{deixai}, the compressed verb \textit{esemanen}, the participle \textit{aposteilas}, the servants, the timing phrase \textit{en tachei}, and John's testimony.

Second comes ellipsis. The passage must be examined not only for what it says explicitly, but also for what it leaves unexpressed. Ellipsis is not a defect in the text. It is a feature of compressed communication. But ellipsis becomes dangerous when interpreters supply missing constituents without rules. The book will therefore treat ellipsis as evidence to be governed, not as an inconvenience to be smoothed away.

Third comes structure. The later chapters will argue that the opening contains seven core verbal heads and that six transmission phrases form a chiastic nucleus. That claim must be built from the surface form; it cannot be assumed. If the structure is real, it will explain why certain missing dependents can be recovered and why certain familiar readings are excluded. If the structure fails, the larger conclusions fail with it.

Fourth comes intertextuality. Revelation is saturated with earlier Scripture, and no serious reading can ignore that. But intertextuality should not be used too early to rescue a decision that the local structure has not justified. Echoes and allusions matter most when they clarify what the passage's own grammar and arrangement have already put into view.

Fifth comes theology. Theology is not irrelevant. The book of Revelation is a theological work, and its opening speaks of God, Jesus Christ, servants, testimony, prophecy, blessing, and obedience. But theological coherence cannot be allowed to replace textual constraint. A reading should not be chosen merely because it fits what the interpreter already expects God, Jesus Christ, angels, John, and the churches to do.

This order does not remove judgment from interpretation. It disciplines judgment. It asks the reader to follow a process: observe the surface form, identify the compression, test the structure, recover what the structure permits, and only then draw consequences. That process will not give every answer immediately. It will sometimes delay the most interesting conclusion until the evidence has been prepared.

The next part of the book begins that slower work. Chapter 4 turns to the reduced form itself, the compact Greek surface form on which smooth translations and familiar interpretations are built. Before the expanded form can be presented, the reduced form must be seen.
