\chapter{The Expanded Form}

\section{Reduced And Expanded Forms}

The previous chapters have moved slowly for a reason. The expanded form should not appear before the reader has seen the problem it solves. Chapter 4 presented the reduced form. Chapter 5 identified the core heads. Chapter 6 showed the ellipses and underdetermined relations. Chapter 7 argued that the six transmission heads form a chiasm that governs recoverability.

The expanded form can now be stated. It is not a paraphrase and it is not a replacement text. It is an analytical reconstruction. Its purpose is to show what the reduced form contains when the recoverable dependents are reinstated according to the rules already argued.

The reduced form of the transmission sequence is given here in transliteration. Its key opening phrase is \textgreek{ἀποκάλυψις Ἰησοῦ Χριστοῦ} (\textit{apokalypsis Iesou Christou}, \textit{disclosure of Jesus Christ}), and its core movement runs through the heads already introduced from the Greek in the preceding chapters.

\begin{quote}
\textit{Apokalypsis Iesou Christou hen edoken auto ho theos deixai tois doulois autou ha dei genesthai en tachei, kai esemanen aposteilas dia tou angelou autou to doulo autou Ioanne, hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou hosa eiden.}
\end{quote}

On this analysis, the expanded form is:

\begin{quote}
\textit{[Ton logon tou theou kai ten martyrian Iesou Christou] apokalypsis Iesou Christou hen edoken auto ho theos deixai tois doulois autou ha dei genesthai en tachei, kai [tois doulois autou ha dei genesthai en tachei] esemanen aposteilas [hen] dia tou angelou autou to doulo autou Ioanne, hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou hosa eiden.}
\end{quote}

The brackets mark supplied constituents. They do not mark new words added for stylistic fullness. They mark elements recovered from corresponding phrases in the structure. The first bracket supplies the content side of the opening disclosure from the A' testimony phrase. The second bracket supplies the recipient and content of \textit{esemanen} from the C phrase. The third bracket supplies the object of \textit{aposteilas} from the B phrase.

The same reconstruction can be displayed more clearly line by line:

\begin{center}
\begin{longtable}{@{}p{0.1\textwidth}p{0.78\textwidth}@{}}
\toprule
Pair & Expanded line \\
\midrule
A & \textit{[ton logon tou theou kai ten martyrian Iesou Christou] apokalypsis Iesou Christou} \\
B & \textit{hen edoken auto ho theos} \\
C & \textit{deixai tois doulois autou ha dei genesthai en tachei} \\
C' & \textit{kai [tois doulois autou ha dei genesthai en tachei] esemanen} \\
B' & \textit{aposteilas [hen] dia tou angelou autou to doulo autou Ioanne} \\
A' & \textit{hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou hosa eiden} \\
\bottomrule
\end{longtable}
\end{center}

This display keeps \textit{hosa eiden} without \textit{te}. Some textual traditions include \textit{te}, but the present reconstruction does not depend on that longer reading. John seeing remains the extranuclear reception element attached to the testimony clause. The structure must work from the critical-text form already used in Chapter 4.

\section{Every Supplied Constituent}

Every supplied constituent must be accounted for. If the expanded form adds more than the structure licenses, it fails the method proposed in this book.

The first supplied constituent is \textit{ton logon tou theou kai ten martyrian Iesou Christou}, the word of God and the testimony of Jesus Christ. It is supplied to the opening head \textit{apokalypsis}. The license is the A / A' pair. \textit{Apokalypsis} and \textit{emartyresen} are both communication terms with a truth-claim dimension. The A phrase is compact. The A' phrase is full. It names the contents to which John testified. The expanded form therefore reads the opening disclosure in relation to the same truth-claim contents.

This supply does not mean that \textit{apokalypsis} and \textit{emartyresen} are synonyms. Disclosure and testimony remain distinct. The point is that the content side of the disclosure is not decided by a detached title reading. It is governed by the corresponding testimony phrase.

The second supplied constituent is \textit{tois doulois autou ha dei genesthai en tachei}, to his servants the things that must happen in speed. It is supplied to \textit{esemanen}. The license is the C / C' pair. \textit{Deixai} and \textit{esemanen} are both communication terms directed toward consciousness. The C phrase states both recipient and content. The C' phrase states only the act of signifying. The pair therefore supplies the missing recipient and content: the same things that are shown to the servants are also signified to the servants.

This is the strongest and most direct reinstatement. It uses a fuller corresponding phrase to fill a bare corresponding phrase. It also preserves the distinction between showing and signifying. The things that must happen are not merely shown; on this analysis, they are also signified.

The third supplied constituent is \textit{hen}, which. It is supplied to \textit{aposteilas} as the object of sending. The license is the B / B' pair. \textit{Edoken} and \textit{aposteilas} are both transfer terms. The B phrase states the object of giving with \textit{hen}. The B' phrase states the mediated sending through the angel to John, but the object of sending is not explicitly repeated. The pair supplies that object: what God gave is also what is sent through the angel to John.

This supply is more complex than the C / C' supply because giving and sending are complementary transfer acts rather than identical acts. The reconstruction therefore does not mechanically copy every dependent from B into B'. It supplies the recoverable object because the corresponding transfer phrase already expresses it.

The expanded form also clarifies what is not supplied. The system does not insert a new explicit subject before \textit{deixai}. It does not replace \textit{auto} with a printed noun inside the Greek line. It does not force \textit{eiden} into the chiastic nucleus. It does not add \textit{te} to the final clause. Those decisions matter. A disciplined reconstruction must leave some questions for the consequence chapters rather than pretending that every conclusion has the same evidential status at the same point.

Still, the supplied constituents have consequences. Once the content of \textit{apokalypsis} is related to the word of God and testimony of Jesus Christ, the opening term cannot be treated as a bare book title. Once \textit{esemanen} receives the same content and recipient as \textit{deixai}, signifying cannot be flattened into a vague summary. Once \textit{aposteilas} receives the object supplied from \textit{edoken}, the sending phrase becomes structurally tied to the giving phrase rather than merely attached to a familiar linear chain.

\section{How The Expanded Form Changes The Reading}

The expanded form changes the reading in four major areas: content, agency, audience, and sequence.

First, it changes the content of the opening. The familiar reading often treats \textit{apokalypsis Iesou Christou} as the controlling title: the revelation of Jesus Christ, from Jesus Christ, or about Jesus Christ. The expanded form does not allow the opening phrase to remain detached from John's testimony. The disclosure is structurally related to the word of God and the testimony of Jesus Christ. That does not yet finish the translation problem, but it changes the question. Chapter 9 will therefore ask what \textit{apokalypsis} should mean if it is governed by this structure rather than by the inherited English title.

Second, it changes agency. The familiar chain often moves from God to Jesus Christ to angel to John to churches. The expanded form makes that chain less secure. The giving phrase and sending phrase correspond as transfer phrases. The showing phrase and signifying phrase correspond as communication phrases. God is explicit in the giving phrase, and the structure requires the signifying phrase to be read in relation to the showing phrase rather than simply absorbed into the usual Jesus-to-angel chain. Chapter 10 will return to the agency question directly, especially the referent of \textit{auto}.

Third, it changes the audience. The servants are not merely a general Christian audience supplied from the later church setting. In the expanded form, the servants are the recipients of both showing and signifying. That makes \textit{tois doulois autou} structurally central rather than incidental. Chapter 11 will therefore have to ask who these servants are within the communication structure, not only who later reads the book.

Fourth, it changes sequence. The surface order is not automatically the event order. Chiasm can arrange elements by correspondence rather than chronology. Giving and sending correspond. Showing and signifying correspond. Disclosure and testimony correspond. The expanded form therefore prevents the reader from assuming that the sentence simply describes a straight line from God to Jesus Christ to angel to John. Some parts of the sequence may be logical, structural, or reciprocal rather than merely chronological.

These changes should not be overstated. Chapter 8 does not answer every consequence. It gives the reconstructed form from which the consequence chapters must now work. The next part of the book will test the major results one at a time: what \textit{apokalypsis} means, who receives what from whom, who the servants are, how \textit{en tachei} should be read, how showing and signifying relate, and what John's testimony contains.

The important result is that the expanded form is no longer a list of interesting possibilities. It is a structured claim. If the chiasm holds, then the supplied constituents are not optional decorations. They are recoverable parts of the reduced form. If the supplied constituents hold, then the familiar reading of Revelation 1:1--3 must be reopened from the beginning.
