\chapter{Ellipsis As Evidence}

\section{What Ellipsis Does}

Chapter 5 identified the core verbal heads in Revelation 1:1--2. That identification was necessary because ellipsis cannot be studied everywhere at once. The question is not whether the opening contains compressed expression. It plainly does. The question is whether that compression is governed.

Ellipsis occurs when something expected for full expression is omitted because it is recoverable. Ordinary speech uses ellipsis constantly. If someone says, ``John received the letter, and Mary the report,'' the second clause does not repeat ``received.'' The missing verb is not a mistake. It is recoverable because the structure supplies it. The hearer does not invent a new action for Mary. The hearer carries forward the action already given.

That ordinary example shows both the usefulness and the danger of ellipsis. Ellipsis is useful because it allows language to be compact. It avoids needless repetition. It lets corresponding phrases work together. But ellipsis is dangerous for interpretation because the missing material must be supplied from somewhere. If the structure supplies it, the interpretation is constrained. If the interpreter supplies it from preference, habit, or theological expectation, the interpretation may become smooth without becoming governed.

This distinction is essential for Revelation 1:1--3. The opening contains several phrases where readers instinctively add what is not fully expressed. They identify pronouns, assign subjects, supply objects, infer recipients, and connect participles to finite verbs. Much of that work happens so quickly that it can feel like reading rather than interpretation. But it is interpretation.

This chapter therefore treats ellipsis as evidence. An ellipsis is not merely a gap to be filled. It is a sign that the passage expects recoverability. The interpreter must ask where the recovery comes from. Does the immediate phrase supply it? Does a corresponding phrase supply it? Does the larger sequence supply it? Does translation tradition supply it? Or does the reader supply it because a familiar line of communication has already been assumed?

The governing principle is simple: omitted constituents should be recovered from textual controls before they are supplied from interpretive convenience. That principle does not yet tell us which structure governs Revelation 1:1--3. It only states the demand. If the opening is elliptical, the missing elements must be recovered by a rule that can be stated, repeated, and tested.

\section{The Ellipses In Revelation 1:1--3}

The ellipses become clearest when the seven heads from Chapter 5 are read as phrase heads. Some phrases are relatively full. Others are highly compressed. The difference matters.

\begin{center}
\begin{longtable}{@{}p{0.18\textwidth}p{0.36\textwidth}p{0.34\textwidth}@{}}
\toprule
Head & Surface phrase & What remains to be supplied or related \\
\midrule
\textit{apokalypsis} & \textit{apokalypsis Iesou Christou} & The genitive relation must be determined. \\
\textit{edoken} & \textit{hen edoken auto ho theos} & The referent of \textit{auto} must be identified. \\
\textit{deixai} & \textit{deixai tois doulois autou ha dei genesthai en tachei} & The subject of showing is not newly expressed. \\
\textit{esemanen} & \textit{kai esemanen} & Subject, object, and recipient are not fully expressed. \\
\textit{aposteilas} & \textit{aposteilas dia tou angelou autou to doulo autou Ioanne} & The sender, the thing sent, and the participle's relation to \textit{esemanen} must be determined. \\
\textit{emartyresen} & \textit{hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou} & The relation of the two testimony objects must be determined. \\
\textit{eiden} & \textit{hosa eiden} & The relation between what John saw and what John testified must be determined. \\
\bottomrule
\end{longtable}
\end{center}

The most obvious ellipsis is \textgreek{καὶ ἐσήμανεν} (\textit{kai esemanen}, \textit{and he signified}). The verb gives an act of signifying, but the surface form does not give the full explicit set of dependents expected in analysis. The reader wants to know who signified, what was signified, and to whom it was signified. A smooth translation can answer these questions, but the Greek surface form has not printed all the answers in the phrase itself.

\textit{Esemainen} is therefore a test case. If the interpreter supplies ``Jesus Christ made it known to John,'' the phrase becomes easy to read. But that supply depends on prior decisions: that \textit{auto} refers to Jesus Christ, that Jesus Christ is the one who shows, that the same linear subject carries forward, and that John is the recipient at this point in the sequence. Those decisions may be possible. They are not yet governed merely because they are possible.

The participle \textgreek{ἀποστείλας} (\textit{aposteilas}, \textit{having sent}) creates a second pressure point. The phrase includes \textgreek{διὰ τοῦ ἀγγέλου αὐτοῦ} (\textit{dia tou angelou autou}, \textit{through his angel}) and \textgreek{τῷ δούλῳ αὐτοῦ Ἰωάννῃ} (\textit{to doulo autou Ioanne}, \textit{to his servant John}). Yet several questions remain. Who sends? What is sent? Is the angel the one sent, the means through whom something is sent, or part of a more complex mediation? How does the participle relate to \textit{esemanen}: does it explain the means of signifying, the timing of signifying, or the larger transfer pattern?

The infinitive \textgreek{δεῖξαι} (\textit{deixai}, \textit{to show}) is less bare, but it is still compressed. The servants and the content are expressed: the disclosure is given to show the servants the things that must happen in speed. But the subject of showing is not introduced as a fresh explicit noun. If Jesus Christ has already been made the recipient of what God gives, then Jesus Christ can easily become the one who shows. If the prior decision changes, the showing relation changes with it.

The opening phrase also contains a different kind of recoverability problem. \textit{Apokalypsis Iesou Christou} is not elliptical in the same simple way as ``and he signified.'' The words are present. The relation is not. The genitive relation must be supplied or construed. The phrase can be read as source, content, possession, association, or a layered relation. This is not ellipsis in the narrowest sense of a missing word, but it belongs to the same methodological problem: the surface form requires a relation that must be governed.

The final testimony clause adds another kind of compression. John \textit{emartyresen}, testified, to the word of God and the testimony of Jesus Christ. Then the clause ends with \textit{hosa eiden}, what he saw. The reader must decide whether what John saw summarizes the preceding objects, explains them, stands in apposition to them, adds a visual component, or functions in some other relation. The surface form forces the question; a smooth rendering often settles it before the reader notices the decision.

Verse 3 is less central to the ellipsis problem being isolated here, but it confirms the broader pattern. The reader, hearers, and keepers receive what is written. The opening is not only about heavenly communication to John. It is also about written prophecy received by a community. That reception frame will matter later, but the densest ellipses remain in the compressed sequence of verses 1--2.

\section{How Interpreters Supply What Is Missing}

Interpreters and translators have to supply what is missing. There is no way around this. Even a highly literal translation must decide how the parts relate. The issue is not whether supply happens. The issue is whether the supply is controlled.

The common modern pattern supplies the opening as a linear chain. God gives the disclosure to Jesus Christ. Jesus Christ shows it to his servants. Jesus Christ makes it known by sending his angel to John. John then testifies to what he saw. That pattern is coherent, and many translations make it easy to read. Some render \textit{esemanen} with a broad expression such as ``made known.'' Some make \textit{aposteilas} the means by which that making known occurs. Some explicitly render the genitive as source by saying the disclosure is from Jesus Christ. Others preserve ``of Jesus Christ'' but still arrange the following clauses so that the same chain is implied.

That pattern supplies several elements at once.

\begin{center}
\begin{longtable}{@{}p{0.26\textwidth}p{0.31\textwidth}p{0.31\textwidth}@{}}
\toprule
Decision point & Common supply & Methodological question \\
\midrule
\textit{auto} & Jesus Christ & Is the nearest familiar antecedent enough, or does structure decide? \\
\textit{deixai} & Jesus Christ shows & Is the subject supplied from the pronoun decision or from another control? \\
\textit{esemanen} & Jesus Christ made it known & Are subject and object recovered from the text or from the assumed chain? \\
\textit{aposteilas} & By sending his angel to John & Does the participle itself identify what is sent and how sending functions? \\
\textit{tois doulois autou} & Christian servants generally & Is the audience determined by the phrase or by the later church setting? \\
\textit{hosa eiden} & The content John reports & How is sight related to testimony, word, and testimony of Jesus Christ? \\
\bottomrule
\end{longtable}
\end{center}

The problem is cumulative dependency. If the first supply is accepted, the second becomes easier. If the second is accepted, the third becomes easier. By the time the interpreter reaches \textit{esemanen} and \textit{aposteilas}, the linear chain may feel established. But it may be established because each uncertain point has been supplied in the direction of the same assumed sequence.

This does not make the common reading foolish. It makes it under-governed unless the interpreter can explain why the supplies are required. The linear chain may still be possible. Chapter 6 is not yet excluding it. The point is that possibility is not enough. The missing or underdetermined elements must be recovered by a system that can say why one supply is legitimate and another is not.

The same problem appears in reverse if an alternative reading is proposed too quickly. It would be no better simply to supply different subjects, objects, or recipients because they serve a preferred conclusion. A non-mainstream reading is not automatically more disciplined. It must obey the same demand: every supplied constituent must be licensed by the surface form and by a stated rule.

The next chapter therefore asks the necessary structural question. The seven heads are not a random list, and the ellipses are not isolated accidents. But to move from that observation to reconstruction, the passage must provide a recoverability structure. If it does not, the system cannot proceed. If it does, that structure must explain what may be supplied, what may not be supplied, and why.
