\chapter{Seven Core Phrases}

\section{A Noun With Verbal Force}

Chapter 4 ended with a problem of selection. Revelation 1:1--3 contains many words, phrases, and relations. If the analysis treats everything as equally central, the method will become shapeless. If it treats only the familiar translation decisions as central, the Greek surface form will be governed by the English result. The next step is therefore to identify the passage's core verbal heads.

The phrase ``core verbal head'' is an analytic term used in this book. It is not being presented as a standard grammatical label that every grammar already uses in this exact form. A head is the controlling word of a phrase or clause-like unit. A verbal head is a head that names an occurrence, act, event, process, or state in a way that can take participants or dependents. A core verbal head, in this analysis, is a verbal head that participates in the main clause-like movement of Revelation 1:1--3 rather than merely modifying another element.

This definition is intentionally functional. It asks what role a term plays in the passage. Does it carry one of the main acts by which disclosure, transfer, communication, testimony, or reception is represented? Does it organize dependents around itself? Does it belong to the main sequence the opening is building? If so, it may be core. If it only helps define the content inside another phrase, it may be important without being core.

The first difficulty is that the opening word is not formally a verb. The passage begins with \textgreek{ἀποκάλυψις} (\textit{apokalypsis}, \textit{disclosure}), a noun. That must be stated plainly. The argument of this book does not require pretending that \textit{apokalypsis} is a finite verb, an infinitive, or a participle. It is a noun.

But nouns can name occurrences. English does this constantly. A ``gift'' can refer to the thing given, but ``giving'' names the act. A ``testimony'' can refer to the content testified, but it also points to an act of testifying. A ``disclosure'' can refer to disclosed content, but it also names the act or event of disclosing. The same general point matters here. \textit{Apokalypsis} is grammatically nominal, yet semantically it is not inert. It opens the passage by naming a disclosure.

That is why \textit{apokalypsis} must be tested as a verbal or eventive noun. The phrase \textit{apokalypsis Iesou Christou} does not merely label the book. It introduces a disclosure in relation to Jesus Christ. The following relative clause then describes that disclosure as something God gave. The surface form therefore does not let \textit{apokalypsis} sit outside the movement of the sentence. It is the first term around which the rest of the opening begins to organize itself.

This matters for method. If \textit{apokalypsis} is excluded from the core set simply because it is a noun, the analysis will miss the fact that the passage begins with an occurrence term. If it is included without qualification, the analysis may overstate the grammar. The careful claim is narrower: \textit{apokalypsis} is included as a core verbal head because it is an action noun or eventive noun functioning as the first head in the passage's communication sequence. It is not a verb in form. It is verbal in force for the purposes of this analysis.

The rest of the core set is more straightforward in form. \textgreek{ἔδωκεν} (\textit{edoken}, \textit{gave}) is a finite verb. \textgreek{δεῖξαι} (\textit{deixai}, \textit{to show}) is an infinitive. \textgreek{ἐσήμανεν} (\textit{esemanen}, \textit{he signified}) is a finite verb. \textgreek{ἀποστείλας} (\textit{aposteilas}, \textit{having sent}) is a participle. \textgreek{ἐμαρτύρησεν} (\textit{emartyresen}, \textit{he testified}) is a finite verb. \textgreek{εἶδεν} (\textit{eiden}, \textit{he saw}) is a finite verb. Each names an occurrence. Each organizes or implies participants. Each belongs to the opening's movement from disclosure through communication to reception.

\section{Why \textit{Dei Genesthai} Is Treated Separately}

The most obvious objection is that the proposed core set leaves out \textgreek{δεῖ γενέσθαι} (\textit{dei genesthai}, \textit{must happen}). That omission can look suspicious because the phrase is theologically and interpretively important. Revelation 1:1 says that the disclosure concerns \textgreek{ἃ δεῖ γενέσθαι ἐν τάχει} (\textit{ha dei genesthai en tachei}, \textit{the things that must happen in speed}). Any interpretation of the opening must account for those things.

The reason for treating \textit{dei genesthai} separately is not that it is unimportant. It is that it performs a different function from the core heads. The phrase identifies content. It tells the reader what is shown: the things that must happen in speed. It does not name another act in the transmission chain by which the disclosure is given, shown, signified, sent, testified, or received.

The distinction is between transmitted content and transmission acts. The things that must happen are the content being communicated. The core heads name the acts by which communication, transfer, testimony, and reception occur. If that distinction is not maintained, the system will confuse what is transmitted with how transmission happens.

This is especially important because \textit{dei} and \textit{genesthai} are themselves verbal in different ways. \textit{Dei} expresses necessity. \textit{Genesthai} names happening or coming to be. They are not grammatically irrelevant. But in this passage they belong inside a relative clause attached to the things shown. They modify and define the content. They do not form a main step in the passage's communicative movement.

The relation can be stated more simply. In the phrase ``to show his servants the things that must happen,'' the act of showing belongs to the transmission sequence. The things that must happen are what the servants are shown. The necessity and happening are part of that content. The same content may later prove important for other elements in the structure, but the phrase itself does not function as another transmission event.

Treating \textit{dei genesthai} as non-core therefore protects the analysis from inflation. A system can fail not only by noticing too little, but also by counting too much. If every verbal element becomes core, the category stops explaining anything. The goal is not to collect all verbal forms. The goal is to identify the verbal heads that organize the main sequence of disclosure, transfer, communication, testimony, and reception.

This also clarifies the status of verse 3. \textgreek{ἀναγινώσκων} (\textit{anaginoskon}, \textit{reading}), \textgreek{ἀκούοντες} (\textit{akouontes}, \textit{hearing}), \textgreek{τηροῦντες} (\textit{terountes}, \textit{keeping}), and \textgreek{γεγραμμένα} (\textit{gegrammena}, \textit{written}) are crucial for the opening's reception and obedience frame. They show that the communicated content reaches readers and hearers who must keep what is written. But Chapter 5 is identifying the core heads in the dense opening sequence of verses 1--2. Verse 3 will matter when reception and obedience are considered in their broader force.

\section{The Seven Heads}

The seven core verbal heads in Revelation 1:1--2 are these:

\begin{center}
\begin{longtable}{@{}p{0.16\textwidth}p{0.2\textwidth}p{0.2\textwidth}p{0.32\textwidth}@{}}
\toprule
Head & Form & Initial category & Working reason \\
\midrule
\textit{apokalypsis} & noun & communication / truth claim & An eventive noun naming disclosure at the head of the opening. \\
\textit{edoken} & finite verb & transfer & God gives something to someone. \\
\textit{deixai} & infinitive & communication / consciousness & The giving has the purpose of showing the servants. \\
\textit{esemanen} & finite verb & communication / consciousness & The act of signifying is stated but compressed. \\
\textit{aposteilas} & participle & transfer & Sending language participates in the same communicative movement. \\
\textit{emartyresen} & finite verb & communication / truth claim & John testifies to named contents. \\
\textit{eiden} & finite verb & reception & John sees; reception is explicitly named. \\
\bottomrule
\end{longtable}
\end{center}

The first six heads belong to transmission. Transmission here means a communicative or transfer event by which content, message, signification, testimony, or disclosure moves from one participant to another. \textit{Apokalypsis}, \textit{deixai}, \textit{esemanen}, and \textit{emartyresen} are communication terms. \textit{Edoken} and \textit{aposteilas} are transfer terms. Together they make the opening more than a title and more than a simple report. They form a sequence of communicative movement.

\textit{Eiden} is different. It is still a core verbal head because it is not a minor decorative detail. It names John's reception of what is communicated. But it is extranuclear in relation to the transmission sequence. It stands on the receiving side. The opening does not only say that something is disclosed, given, shown, signified, sent, and testified. It also says that John saw. Any system that explains transmission but cannot explain reception has not explained the whole opening.

The seven heads can also be grouped by the kind of occurrence they name. \textit{Edoken} and \textit{aposteilas} are transfer occurrences. They involve movement from one party toward another. \textit{Deixai} and \textit{esemanen} are communication occurrences that affect consciousness: something is shown or signified so that it may be perceived or understood. \textit{Apokalypsis} and \textit{emartyresen} are communication occurrences with a truth-claim dimension: disclosure and testimony both concern what is made known or attested as true. \textit{Eiden} names reception, the seeing by which John is brought into relation with what is communicated.

This grouping is not yet the chiasm. That argument comes later. At this stage the claim is more modest and more basic: the heads are not a random list. They are selected by function. They are occurrence terms. They organize the main movement of the opening. They distinguish transmission from reception. They also prevent the analysis from treating every verbal form as equally central.

Each head governs or implies a phrase.

\begin{center}
\begin{longtable}{@{}p{0.18\textwidth}p{0.36\textwidth}p{0.34\textwidth}@{}}
\toprule
Head & Surface phrase & Immediate pressure \\
\midrule
\textit{apokalypsis} & \textit{apokalypsis Iesou Christou} & What relation does ``of Jesus Christ'' express? \\
\textit{edoken} & \textit{hen edoken auto ho theos} & Who is the recipient of what God gave? \\
\textit{deixai} & \textit{deixai tois doulois autou ha dei genesthai en tachei} & Who shows, and what exactly is shown? \\
\textit{esemanen} & \textit{kai esemanen} & Who signified, what was signified, and to whom? \\
\textit{aposteilas} & \textit{aposteilas dia tou angelou autou to doulo autou Ioanne} & Who sends, what is sent, and how does sending relate to signifying? \\
\textit{emartyresen} & \textit{hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou} & How do the named testimony objects relate? \\
\textit{eiden} & \textit{hosa eiden} & How does what John saw relate to what John testified? \\
\bottomrule
\end{longtable}
\end{center}

This second table shows why identifying the heads matters. The heads are not merely vocabulary items. They expose the points where the surface form is compressed. The giving has an explicit giver but a pronoun whose referent must be decided. The showing has a stated audience and content but no newly expressed subject. The signifying is especially bare. The sending has attached phrases but still requires its relation to the larger clause. The testimony names objects whose relation must be clarified. The seeing must be integrated with testimony rather than treated as an afterthought.

This is the bridge from Chapter 5 to Chapter 6. Once the core heads have been identified, the ellipses are easier to see. The passage is not merely difficult because readers disagree about meanings. It is difficult because several of the main heads require supplied or related dependents. The next chapter therefore turns directly to ellipsis, not as an embarrassment in the text, but as evidence that must be governed.
