\chapter{Who Receives What From Whom?}

\section{The Referent Of \textit{Auto}}

The familiar reading of Revelation 1:1 depends heavily on one small word: \textgreek{αὐτῷ} (\textit{auto}, \textit{to him}). In the common linear chain, God gives the disclosure to Jesus Christ. Jesus Christ then shows it to his servants, makes it known by sending his angel to John, and John passes it on to the churches. That reading is coherent. It is also easy to understand because Jesus Christ has just been named in \textit{apokalypsis Iesou Christou}.

But the system argued in the previous chapters does not allow \textit{auto} to be decided by proximity alone. The pronoun belongs to the B phrase:

\begin{quote}
\textit{Iesou Christou hen edoken auto ho theos}
\end{quote}

That B phrase corresponds to the B' phrase:

\begin{quote}
\textit{aposteilas [hen] dia tou angelou autou to doulo autou Ioanne}
\end{quote}

The two phrases are transfer phrases. B names giving. B' names sending. B explicitly names God as giver and the disclosure as what is given. B' names mediated transfer through the angel and identifies the endpoint as John: \textit{to doulo autou Ioanne}, to his servant John. The corresponding transfer phrase therefore supplies the strongest structural control for the recipient in B.

On this analysis, \textit{auto} refers to John.

This conclusion is not reached because John is the nearest antecedent. He is not. It is reached because the B / B' pair places the giving and sending phrases in correspondence. The giving phrase says that God gave the disclosure ``to him.'' The sending phrase says that the disclosure was sent through the angel ``to his servant John.'' Since the paired transfer phrase names John as the endpoint, John is the structurally governed referent of the pronoun.

This excludes the familiar reading for this passage. Jesus Christ remains central to the opening, but he is not the recipient named by \textit{auto}. The disclosure is not first given by God to Jesus Christ so that Jesus Christ can then pass it down the chain. Rather, the transfer pair identifies John as the recipient of what God gives and what God sends through his angel.

The result also changes the role of \textit{Iesou Christou} in the B phrase. If \textit{auto} does not refer to Jesus Christ, then the phrase \textit{Iesou Christou} cannot function merely as the antecedent that launches the familiar chain. It must be read in relation to the opening \textit{apokalypsis Iesou Christou} and to the corresponding B' phrase, especially \textit{dia tou angelou autou}. That relation will matter throughout the rest of the agency question.

\section{The Subject Of Showing}

Once \textit{auto} is no longer Jesus Christ, the subject of \textit{deixai} must be reconsidered. The familiar reading commonly lets the first decision control the second: if God gave the disclosure to Jesus Christ, then Jesus Christ becomes the one who shows it to his servants. But if God gave the disclosure to John, that chain no longer governs the infinitive.

The phrase is:

\begin{quote}
\textit{deixai tois doulois autou ha dei genesthai en tachei}
\end{quote}

The phrase gives the audience and content: the servants are shown the things that must happen in speed. It does not introduce a fresh explicit subject for the showing. Chapter 6 identified that compression. Chapter 7 argued that \textit{deixai} corresponds to \textit{esemanen}. Chapter 8 then supplied the recipient and content of \textit{esemanen} from \textit{deixai}. The remaining question is subject.

The nearest explicit subject before the showing phrase is \textit{ho theos}, God. God gives the disclosure. The same God is also the subject naturally carried into the following finite verb \textit{esemanen}: ``and he signified.'' If \textit{esemanen} belongs to the C / C' pair with \textit{deixai}, then showing and signifying are paired acts in the same communication field. The subject should not be changed without structural reason.

On this analysis, God is the one who shows and the one who signifies.

This does not erase mediation. The sending phrase still says that God acts \textit{dia tou angelou autou}, through his angel. But mediation is not the same as agency transfer. A messenger can be the means through whom the giver sends without becoming the ultimate subject of every communication verb. The surface form explicitly names God as giver. The paired structure keeps God as the controlling agent of showing and signifying.

This also explains why \textit{deixai} and \textit{esemanen} must not be flattened. If Jesus Christ is assumed to receive, show, signify, and send, the verbs can collapse into a general act of making known. But the structure separates the acts. God gives. God shows the servants what must happen in speed. God signifies the same things to the same servants. God sends the disclosure through his angel to John. The acts are related, but they are not interchangeable.

The subject of showing therefore follows the same discipline as the referent of \textit{auto}. It is not decided by the smoothest traditional chain. It is decided by the local syntax and by the corresponding pairs. Once those controls are allowed to operate, Jesus Christ is not the subject of \textit{deixai} in this passage.

\section{God As Shower And Signifier}

The resulting agency pattern can now be stated more directly. In the reduced form, God is explicitly the giver:

\begin{quote}
\textit{hen edoken auto ho theos}
\end{quote}

In the expanded form, God remains the governing agent of the communication sequence:

\begin{quote}
God gave the disclosure to John, to show his servants the things that must happen in speed, and God signified those things to his servants, having sent the disclosure through his angel to his servant John.
\end{quote}

This English sentence is not being offered as a polished translation. It states the structural result. The point is agency. God is not merely the distant source at the beginning of a chain that Jesus Christ then controls. God is the giver, the one who shows, and the signifier.

The transfer pair also identifies the mediation more sharply. B contains \textit{Iesou Christou}; B' contains \textit{dia tou angelou autou}. Since B and B' correspond, the phrase ``through his angel'' cannot be treated as an unrelated detail. On this analysis, the angel through whom God sends the disclosure is Jesus Christ.

That claim must be stated carefully. It does not mean the system has imported a general angel-Christ theology from outside the passage. It means that within this structure, the Jesus Christ named in the opening transmission sequence corresponds to the angel in the sending phrase. The passage's own transfer pair creates the identification. God sends the disclosure through his angel, Jesus Christ, to John.

This changes the familiar chain. The common sequence is:

\begin{quote}
God $\rightarrow$ Jesus Christ $\rightarrow$ angel $\rightarrow$ John $\rightarrow$ servants or churches.
\end{quote}

On this analysis, the structure is better represented as:

\begin{quote}
God gives and communicates the disclosure; God sends it through his angel, Jesus Christ, to John; the things that must happen are shown and signified to the servants; John testifies to the word of God, the testimony of Jesus Christ, and what he saw.
\end{quote}

This model is less simple than the familiar chain, but it explains more of the reduced form with fewer arbitrary supplies. It explains why \textit{auto} should be read with John as its referent. It explains why \textit{esemanen} receives its content and recipients from \textit{deixai}. It explains why \textit{aposteilas} receives its object from \textit{edoken}. It explains why Jesus Christ remains central without making him the recipient of what God gives.

The chapter should not end by pretending that every related question has been settled. The identity of the servants now becomes more important, not less. If God shows and signifies the things that must happen to his servants, and if John is the servant who receives the disclosure through the angel, then the servants cannot simply be treated as a vague synonym for all later Christian readers. They must be located within this communication structure. That is the next question.
