\chapter{The Trouble With Plausible Readings}

Many standard interpretations of Revelation 1:1--3 are plausible. That is precisely the problem. Plausibility can show that a reading may be allowed, but it does not by itself show why that reading should be chosen over another plausible reading.

\section{\textit{Apokalypsis Iesou Christou}}

The first phrase introduces the first plausible reading: \textgreek{ἀποκάλυψις Ἰησοῦ Χριστοῦ} (\textit{apokalypsis Iesou Christou}, \textit{disclosure of Jesus Christ}). In English, ``of Jesus Christ'' can sound harmlessly broad. It can even preserve some ambiguity. But readers rarely leave it ambiguous for long. They tend to hear a relation: a revelation from Jesus Christ, a revelation about Jesus Christ, a revelation belonging to Jesus Christ, or a revelation in which Jesus Christ is both source and content.

Greek permits more than one relation here. That fact is not controversial in itself. The issue is what happens next. If the phrase can be read in more than one way, then the interpreter must decide what kind of evidence determines the relation. Does the decision come from the immediate grammar? From the following clause? From the assumed chain of communication? From the theology of the book as a whole? From the use of similar genitives elsewhere? From what sounds most natural after centuries of reading the book as ``the Revelation of Jesus Christ''?

Each route can produce a plausible answer. If the next clause is taken to mean that God gave the disclosure to Jesus Christ, then \textit{Iesou Christou} naturally sounds like source or mediation: the disclosure comes through Jesus Christ. If the book is read as a disclosure of Jesus Christ's identity, victory, and rule, then the phrase can sound objective: the disclosure is about Jesus Christ. If the opening phrase is treated as a title-like label, then ``of Jesus Christ'' can be left broad enough to include ownership or association.

The trouble is not that these readings are foolish. The trouble is that the grammar alone does not select one of them. A reading can be grammatically possible, contextually attractive, and theologically comfortable, yet still remain underdetermined. The opening phrase therefore introduces the basic problem of the book: Revelation 1:1--3 does not merely contain difficult meanings; it contains decisions whose governing rules must be made explicit.

This matters especially because \textit{apokalypsis} itself is not a neutral English problem. The common rendering ``revelation'' brings assumptions with it. In ordinary English, revelation often suggests something previously hidden, unknown, or concealed that is now made known. The later argument of this book will test whether that sense can survive the structure of the opening. For now, the important point is smaller: before the reader has reached the second phrase, interpretation has already begun.

\section{\textit{Hen Edoken Auto Ho Theos}}

The next phrase seems to settle the matter: \textgreek{ἣν ἔδωκεν αὐτῷ ὁ θεός} (\textit{hen edoken auto ho theos}, \textit{which God gave to him}). If the disclosure is ``of Jesus Christ,'' and if God gave it ``to him,'' the familiar reading identifies ``him'' as Jesus Christ. That reading is easy to understand. Jesus Christ has just been named. The sequence God gives to Jesus Christ, Jesus Christ shows to his servants, Jesus Christ sends through an angel to John has become so familiar that the pronoun appears almost self-explanatory.

But a pronoun is not self-explanatory simply because one antecedent is nearby. A pronoun must be interpreted within the structure in which it appears. The phrase tells us that God gave something to someone. It does not, by itself, explain the full communication chain, the relation of the giving to the showing, the relation of the showing to the signifying, or the relation of the sending to John. Those relations are supplied by interpretation.

The familiar reading is plausible because it creates a smooth line. God gives the disclosure to Jesus Christ; Jesus Christ shows it to his servants; Jesus Christ makes it known by sending his angel to John. That line is coherent. It is also the line many English translations encourage. But coherence is not enough. The question is whether the pronoun has been decided by the grammar and structure of the passage or by the smoothness of the line that results.

This is where the opening begins to show its compression. If \textit{auto} refers to Jesus Christ, then Jesus Christ becomes the receiver of what God gives and, in most readings, the one who then shows and signifies. But if the pronoun is read differently, the whole chain changes. The identity of the receiver affects the identity of the one who shows, the signifier, the sender, the angel, the servant John, and the relation between the book and the disclosure. A small pronoun controls a large interpretation.

The point in this chapter is not yet to prove the alternative. That comes later, when the structure of the passage is examined. The point is that the usual decision is not innocent. It is possible, but it carries consequences. The interpreter should therefore be able to say why this pronoun must be read that way and why competing possibilities are excluded.

\section{Showing, Signifying, And Sending}

The pressure increases with the verbs of communication and transfer. God gives the disclosure \textgreek{δεῖξαι} (\textit{deixai}, \textit{to show}) to his servants what must take place. Then the text says \textgreek{καὶ ἐσήμανεν} (\textit{kai esemanen}, \textit{and he signified}). Then it adds \textgreek{ἀποστείλας} (\textit{aposteilas}, \textit{having sent}) through his angel to his servant John.

In a smooth reading, these words are usually absorbed into the same linear chain. Jesus Christ shows, makes known, and sends through an angel. Or God gives to Jesus Christ, and Jesus Christ then communicates through the angel to John. The surface form can be made to read that way. But the Greek is more compressed than that account suggests.

The infinitive \textit{deixai} gives a purpose: the disclosure is given ``to show'' something to the servants. Yet the subject of the showing is not expressed as an independent noun in that phrase. The interpreter must decide who does the showing. If Jesus Christ has just been made the receiver of the disclosure, then Jesus Christ can easily become the one who shows. But that conclusion depends on the prior decision about \textit{auto}. It is not an isolated grammatical fact.

The verb \textit{esemanen} is even more compressed. The text says ``and he signified,'' but the English reader immediately wants more: who signified, what was signified, and to whom? A translation may smooth the verb as ``made known,'' but the smoothing does not answer the structural question. The verb still needs a subject and an object in the analysis, and those dependents must be supplied from somewhere. If the interpreter supplies them from the already assumed linear chain, the chain begins to confirm itself.

The participle \textit{aposteilas} raises a related problem. It can be rendered ``having sent'' or ``by sending,'' but what exactly does the participle modify? Who sends? What or whom is sent? Is the angel the one sent, the means through whom something is sent, or part of a larger mediation pattern? Again, a smooth English sentence can make the answer feel obvious. The Greek surface form still requires analysis.

These three terms matter because they are not synonyms. Showing is not identical to signifying, and signifying is not identical to sending. If they are collapsed into a general idea of ``making known,'' the reader loses distinctions that may be structurally important. The later argument of this book will claim that the things that must take place are not only shown; they are also signified. Chapter 2 does not yet prove that claim. It only shows why the verbs cannot be flattened before the structure has been examined.

Here the problem of plausibility becomes more serious. A reading may be plausible at each step: Jesus Christ receives, Jesus Christ shows, Jesus Christ signifies, Jesus Christ sends. But if every later decision depends on the first smooth assumption, then plausibility has become cumulative without becoming governed. The interpretation looks stable because each piece has been made to fit the same line. What remains to be shown is whether the passage itself establishes that line.

\section{Servants And Speed}

The same problem appears in the audience and timing language. The disclosure is given \textgreek{δεῖξαι τοῖς δούλοις αὐτοῦ} (\textit{deixai tois doulois autou}, \textit{to show to his servants}) what must take place \textgreek{ἐν τάχει} (\textit{en tachei}, \textit{in speed}). These phrases are familiar, and familiarity can make them seem simpler than they are.

The servants are often understood as Christians generally. That reading is understandable. The book of Revelation is addressed to churches, and the book is read by Christian communities. The blessing in the next verse includes those who read, hear, and keep what is written. A broad Christian audience is therefore an attractive conclusion.

But the phrase itself says ``his servants.'' It does not immediately define which servants are meant, how wide the category is, or how the servants relate to John, the angel, Jesus Christ, and God. The word servant also carries a relation with a master or lord. It belongs to a frame of command, reception, and obedience. If that frame matters, then the servants cannot be identified only by general religious familiarity. Their place in the transmission structure must be determined.

The timing phrase \textit{en tachei} is equally important. It is often rendered as ``soon'' or ``shortly.'' That is a possible reading, and it has shaped enormous portions of interpretation of the book of Revelation. If the things must happen soon, then the opening appears to make a strong claim about temporal nearness. Readers then ask whether the events were fulfilled near John's time, whether ``soon'' is measured from God's perspective, whether the book stretches imminence across history, or whether some other theological adjustment is needed.

But \textit{en tachei} can also point toward speed or manner: in speed, speedily, quickly. That possibility does not automatically decide the phrase. It does, however, prevent ``soon'' from being treated as if it were the only meaningful option. Once again the issue is not whether the familiar translation is possible. The issue is why it is chosen and what rule excludes the other options.

By the end of the opening sentence, the reader has encountered a series of plausible decisions: what \textit{apokalypsis Iesou Christou} means, who receives what God gives, who shows, who signifies, what is sent, who the servants are, and how \textit{en tachei} should be understood. The usual reading can answer all of these questions. But answering questions is not the same as governing answers.

That is the trouble with plausible readings. They can make a passage readable while leaving the method invisible. The next chapter therefore asks what kind of system would be strong enough to choose among such readings without merely preferring the familiar one.
