\chapter{John's Testimony}

\section{The Word Of God}

The opening transmission sequence does not end with sending. It reaches John and becomes testimony. The surface form of Revelation 1:2 is:

\begin{quote}
\textit{hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou hosa eiden}
\end{quote}

John is the one \textgreek{ἐμαρτύρησεν} (\textit{emartyresen}, \textit{testified}). The verb belongs to the same communication field as disclosure, showing, signifying, and sending, but it adds a truth-claim dimension. A witness does not merely pass along data. A witness bears testimony to what has been received.

The first named object of John's testimony is \textgreek{τὸν λόγον τοῦ θεοῦ} (\textit{ton logon tou theou}, \textit{the word of God}). This phrase must not be treated as ornamental religious language. It is one of the contents to which John testifies, and Chapter 8 already showed that it supplies the content side of the opening \textit{apokalypsis} through the A / A' pair.

The phrase can be heard in more than one way. It can mean the word that comes from God, the word that belongs to God, or the message whose source and authority are God. Those possibilities are not mutually exclusive in this context. The important point is that \textit{logos} is communicative. It points toward word, message, or speech. It is not merely a visual object.

That matters because the final clause names what John saw. If the interpreter begins and ends with \textit{hosa eiden}, ``what he saw,'' the word of God can disappear into a general report of visions. But the Greek surface form does not begin with what John saw. It says first that John testified to the word of God. The visual clause must be related to that object; it should not erase it.

Within the structure argued in this book, the word of God belongs to the same communication system in which God gives, shows, signifies, and sends. John receives the disclosure through the angel and testifies. His testimony is therefore not merely a private memory of visionary experience. It is witness to God's communicated word.

This is the first reason the chapter can speak of hearing as well as seeing. The base text does not say, at this point, ``what John heard.'' But the phrase \textit{ton logon tou theou} names a communicative word or message. It gives the testimony an auditory or verbal dimension that \textit{eiden} alone would not supply. The claim must be modest: the text explicitly names what John saw, and it names the word of God as an object of testimony. On this analysis, John's testimony therefore includes both visual reception and received word.

\section{The Testimony Of Jesus Christ}

The second named object is \textgreek{τὴν μαρτυρίαν Ἰησοῦ Χριστοῦ} (\textit{ten martyrian Iesou Christou}, \textit{the testimony of Jesus Christ}). This phrase is crucial because it repeats the same genitive name that appeared in \textit{apokalypsis Iesou Christou}. The repetition is evidence, not a shortcut.

Many readings decide the first phrase and then carry that decision into the second. If \textit{apokalypsis Iesou Christou} is taken as ``revelation from Jesus Christ,'' then \textit{ten martyrian Iesou Christou} may be taken as testimony from Jesus Christ. If the first is taken as ``revelation about Jesus Christ,'' then the second may be taken as testimony about Jesus Christ. Both readings are grammatically possible. Neither should be chosen merely by habit.

The local context gives stronger controls. John is the subject of \textit{emartyresen}: he testified. The testimony phrase is one of the objects of his testimony. That means John bears witness to the testimony of Jesus Christ. The phrase therefore contains at least two layers: Jesus Christ is bound to the testimony, and John testifies to that testimony.

The agency conclusions from Chapter 10 sharpen the matter. On this analysis, God sends the disclosure through his angel, Jesus Christ, to John. Jesus Christ is not the recipient named by \textit{auto}; he is the mediating angel in the transfer pair. If that is right, then the testimony of Jesus Christ is not an isolated title for Christian doctrine. It belongs to the mediated disclosure that reaches John.

This does not require choosing only one genitive label. The testimony may be Jesus Christ's testimony in the sense that it is borne by him or belongs to him, and it may also concern him because he is central to the disclosure. The structure warns against reducing the phrase to one English preposition too quickly. What matters for the present chapter is that John testifies to this testimony. He is not inventing the witness; he receives and bears it.

The phrase also helps explain why John cannot be treated as a mere scribe. A scribe copies words. A witness testifies to received truth. John is called God's servant, receives the disclosure through the angel, and bears witness to the word of God and the testimony of Jesus Christ. His writing is downstream from testimony, not identical with the original disclosure itself.

This keeps Chapter 9's distinction in place. The book of Revelation is the written work through which John's testimony reaches readers and hearers. The disclosure is the transmitted communicative entity named at the beginning. John's testimony stands between them. It receives the disclosure and becomes the written witness by which later readers encounter it.

\section{What John Heard And Saw}

The final words are \textgreek{ὅσα εἶδεν} (\textit{hosa eiden}, \textit{as much as he saw} or \textit{whatever he saw}). This is the base wording used in the reconstruction. Some textual traditions include \textit{te}, producing \textit{hosa te eiden}. That longer form can make coordination more visible, as though the phrase more clearly adds ``and whatever he saw.'' But the argument here must work from the shorter critical-text form. The system cannot depend on silently importing \textit{te}.

With or without \textit{te}, \textit{eiden} matters. Chapter 7 described it as an extranuclear reception element. It does not belong to the six-head chiastic nucleus in the same way as \textit{apokalypsis}, \textit{edoken}, \textit{deixai}, \textit{esemanen}, \textit{aposteilas}, and \textit{emartyresen}. It confirms that the transmission has reached perception. John saw.

The question is how \textit{hosa eiden} relates to the two preceding objects. It could be read as a summary: John testified to the word of God and testimony of Jesus Christ, that is, everything he saw. It could be read as an appositional clarification. It could be read as adding the visual dimension to the named word and testimony. The shorter text leaves the relation compact.

The structure favors the third approach. The word of God and the testimony of Jesus Christ should not be swallowed by the final visual clause. They are named objects of testimony. At the same time, \textit{hosa eiden} should not be detached as a separate afterthought. It shows how John's reception enters the testimony: what God discloses, shows, signifies, and sends is received by John in visionary perception and then borne as witness.\footnote{This is not only a modern structural concern. Swete treats the word of God and testimony of Jesus Christ as the revelation given by God and attested by Christ, received in vision; Charles also distinguishes the source, contents, and reception of the superscription, with the contents seen by John in vision. \autocites[3]{swete1911apocalypse}[1, 5--6]{charles1920revelation}.}

This means John's testimony includes what he heard and saw, but the two parts are not proved in the same way. Seeing is explicit in \textit{eiden}. Hearing is inferred from the communicative contents: the word of God and the testimony of Jesus Christ. The inference is not arbitrary because the whole passage is a transmission model. God gives, shows, signifies, and sends; John receives and testifies; readers hear and keep what is written.

The A / A' pair now comes into focus:

\begin{center}
\begin{longtable}{@{}p{0.12\textwidth}p{0.74\textwidth}@{}}
\toprule
Pair & Phrase \\
\midrule
A & \textit{[ton logon tou theou kai ten martyrian Iesou Christou] apokalypsis Iesou Christou} \\
A' & \textit{hos emartyresen ton logon tou theou kai ten martyrian Iesou Christou hosa eiden} \\
\bottomrule
\end{longtable}
\end{center}

The opening disclosure and John's testimony correspond as communication and truth-claim acts. The disclosure is not the written book by itself. The testimony is not a decorative report after the real action. The disclosure is transmitted; John receives; John testifies to the word of God, the testimony of Jesus Christ, and what he saw; the written book then brings that testimony to readers and hearers.

This also explains why verse 2 cannot be reduced to ``John wrote down the book of Revelation.'' John does write, and the written work matters. Verse 3 blesses the reader, the hearers, and those who keep what is written. But verse 2 is more basic than the act of writing. It identifies John as witness. His book is the written form of that witness, not the disclosure itself and not a mere transcript detached from reception.

The result completes the consequence sequence begun in Chapter 9. The \textit{apokalypsis} is an eventive disclosure, structurally related to the word of God and testimony of Jesus Christ. God gives, shows, signifies, and sends. The servants receive shown-and-signified content. John, the named servant, receives the disclosure through the angel and testifies to the word, the testimony, and what he saw. The next task is to ask how this reconstructed opening changes the reading frame for the rest of the book.
