\chapter{Shown And Signified}

\section{Showing}

The previous chapter ended with a communication question. If the things that must happen in speed are disclosed to servants, how are they communicated? The opening gives two paired verbs: \textgreek{δεῖξαι} (\textit{deixai}, \textit{to show}) and \textgreek{ἐσήμανεν} (\textit{esemanen}, \textit{he signified}). The two verbs must be held together, but they must not be collapsed.

The first verb is \textit{deixai}. It names showing. In ordinary terms, showing places something before someone so that it can be perceived, recognized, or understood. In the opening phrase, the servants are the recipients and the things that must happen in speed are the content:

\begin{quote}
\textit{deixai tois doulois autou ha dei genesthai en tachei}
\end{quote}

The grammar therefore gives three elements: an act of showing, an audience, and shown content. Chapter 10 argued that God is the subject of this showing. Chapter 11 argued that the recipients are God's servants, not a vague religious audience. Chapter 12 argued that the content is not simply a timetable of soon events, but the things that must happen in speed. The present chapter now asks what happens when those things are shown.

Showing should not be treated as mere information transfer. To show is more concrete than to state. The book of Revelation is full of scenes, voices, actions, measurements, seals, trumpets, bowls, beasts, cities, witnesses, angels, and thrones. The opening does not yet list those later visions, but it prepares the reader for a mode of communication in which the servants are made to see and recognize what God discloses.

This does not mean every act of showing must be visual in the narrowest sense. The book includes hearing as well as seeing. John hears voices and words; he also sees visions. But \textit{deixai} still points toward presentation. Something is displayed, brought before the recipient, or made perceptible. The servants do not receive an abstract proposition only. They receive disclosed realities in a form that can be apprehended.

That matters for interpretation. If the opening said only that God told his servants what must happen, the reader might expect a list of predictions. But the opening says the things are shown. A shown event can be seen from more than one angle. It can be staged, sequenced, repeated, intensified, or represented through images. Showing opens the door to visionary form before the book's later visions have even begun.

\section{Signifying}

The second verb is \textgreek{ἐσήμανεν} (\textit{esemanen}, \textit{he signified}). Many translations render it with a broad phrase such as ``made known.'' That is understandable as a smooth English result, but it loses an important distinction. To signify is not merely to inform. It is to communicate by signs, indications, or marked forms that require recognition.

The surface form is brief:

\begin{quote}
\textit{kai esemanen}
\end{quote}

On its own, that phrase leaves several questions open. Who signified? What was signified? To whom was it signified? Chapter 6 identified this as one of the major ellipses in the opening. Chapter 7 argued that \textit{esemanen} corresponds to \textit{deixai}. Chapter 8 supplied the missing recipients and content from the C phrase. Chapter 10 identified God as the signifier. The expanded form is therefore:

\begin{quote}
\textit{kai [tois doulois autou ha dei genesthai en tachei] esemanen}
\end{quote}

On this analysis, God signified to his servants the things that must happen in speed.

This is not a decorative repetition of showing. If showing and signifying were identical, the second verb would add little to the structure. But the opening uses both. Showing presents the things. Signifying marks, encodes, or indicates them in a way that calls for interpretation.

That distinction helps explain why the book of Revelation is so often difficult. The problem is not merely that later readers lack information. The communicated things are signified. They come through signs, images, correspondences, echoes, and symbolic forms. A beast is not only an animal in a scene. A lampstand is not only an object. A city is not only an urban location. The book's visions show, but they also signify.

This should be stated carefully. ``Signified'' does not mean ``made unreal.'' Symbolic communication is not less serious than literal communication. A sign can refer to real powers, real judgments, real communities, real worship, and real obedience. The question is not whether the things are real. The question is how they are communicated. The opening warns the reader that they are communicated in a signifying mode.

The word also guards against another mistake. Some readings treat the visions as though each image must correspond to one obvious external item. But signifying does not guarantee a simple one-to-one code. Signs can gather associations. They can compress several realities into one image. They can draw on earlier Scripture, liturgical patterns, political realities, and heavenly scenes at the same time. The interpreter must therefore ask what the sign does within the book's own communication system before assigning it a final referent.

\section{The Things That Must Take Place}

The C / C' pair now carries its full weight. The same content is both shown and signified:

\begin{center}
\begin{longtable}{@{}p{0.1\textwidth}p{0.78\textwidth}@{}}
\toprule
Pair & Expanded line \\
\midrule
C & \textit{deixai tois doulois autou ha dei genesthai en tachei} \\
C' & \textit{kai [tois doulois autou ha dei genesthai en tachei] esemanen} \\
\bottomrule
\end{longtable}
\end{center}

This means the things that must happen are not communicated in two unrelated stages. They are the shared content of paired divine acts. God shows them to his servants, and God signifies them to his servants. The structure requires both claims.

The result changes how the later book should be approached. If the things are only shown, the interpreter may emphasize vision and spectacle. If they are only signified, the interpreter may emphasize symbols and codes. The opening gives both. The servants receive visionary presentation and signifying communication. They see things, but what they see must be read as signs. They encounter signs, but those signs are not detached from what God shows.

This helps explain why multiple interpretations arise. The problem is not simply that readers are careless or that the book is obscure for its own sake. A shown-and-signified disclosure creates layered communication. The same image may be visually concrete, theologically charged, scripturally echoed, politically pointed, and ethically directed. Different interpreters may seize different layers. The solution is not to deny the layers, but to govern them.

The opening supplies that governance in seed form. The content is the things that must happen in speed. The recipients are God's servants. The agent is God. The mode is showing and signifying. The mediation runs through the angel to John. John then testifies. The reader and hearers are blessed as they keep what is written. These controls do not make every later image easy, but they do prevent the interpreter from treating the visions as free-floating symbols.

This also prevents a false choice between literal and symbolic readings. The opening does not say, ``These things are either literal events or symbols.'' It says the things that must happen are shown and signified. The happening belongs to the content; the signifying belongs to the communication mode. A signified event can still be an event. A shown reality can still require interpretation.

The next question is therefore John's testimony. If God shows and signifies the things that must happen, and if John is the servant who receives the disclosure through the angel, what exactly does John bear witness to? The answer cannot be reduced to ``what he saw'' alone, even though seeing is essential. The final clause names the word of God, the testimony of Jesus Christ, and what John saw. That is the next relation to test.
